R Notebook

### 2021-06-28 FEM_R/IJM_PAPER1_ALL_ANALYSES.Rmd
Now automatically generate script with all figures after running core_scen

## Libraries
```{r "setup", include=FALSE}
require(tidyverse)
require(haven)
require(ggplot2)
require(Hmisc)

@@

## Heart Disease Intervention
```{r}
compareDeathAge <- function(base, int, int_name, save=FALSE, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

  aDeath <- data.frame(base$year, base$d_age_all, int$d_age_all)

  aDeath <- aDeath %>%
                dplyr::rename('Year' = base.year, 'Baseline' = base.d_age_all, !!quo_name(int_name) := int.d_age_all) %>%
                reshape2::melt(id.var = 'Year', value.name = 'Age')

  p1 <- ggplot(data = aDeath, aes(x = Year, y = Age, color = variable)) +
        geom_smooth(lwd = 0.5, se=FALSE) +
        labs(x = 'Year', y = 'Age at Death') +

  if(save) {
    ggsave(filename = 'hearte_dAge_all.png',
         plot = p1,
         path = path)
  }

  return(p1)
}
```

### Life-Expectancy
```{r}
b <- read_dta('output/SCENARIO/ELSA_core_base/ELSA_core_base_summary.dta')
h_p <- read_dta('output/SCENARIO/ELSA_core_remove_hearte_p/ELSA_core_remove_hearte_p_summary.dta')

compareDeathAge(b, h_p, 'No Heart Disease', save=FALSE)
```

@@

## Smoking Intervention
```{r}
compareSurvivalCurve <- function(cohort, intervention, int_name, save=FALSE,
                                 path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

  # Had a small problem when trying to rename using the variable name given as function argument
  # Found solution here: https://stackoverflow.com/questions/49650394/how-to-rename-a-variable-using-a-dynamic-name-and-dplyr
  #survivals <- survivals %>%
  #               dplyr::rename('Age' = cohort.Age, 'Baseline' = cohort.Survival, !!quo_name(int_name) := intervention.Survival) %>%
  #               melt(id.var = 'Age', value.name = 'Survival')

  survivals <- survivals %>%
                 dplyr::rename('Age' = cohort.Age, 'Rep' = cohort.rep, 'Baseline' = cohort.Survival, !!quo_name(int_name) := intervention.Survival) %>%
                 pivot_longer(
                   cols = Baseline:'No Smoking',
                   names_to = 'Source',
                   values_to = 'Life_Exp'
                 )

  p1 <-ggplot(data = survivals, aes(x=Age, y=Life_Exp, color = Source)) +
        geom_smooth(lwd = 0.5) +
        labs(x = 'Age', y = 'Survival')

  if(save) {
    ggsave(filename = paste0(int_name, '_survival_curve.png'),
         plot = p1,
         path = path)
  }

  return(p1)
}
```

### Survival Curve
```{r}
c <- read_dta('output/SCENARIO/ELSA_core_cohort/ELSA_core_cohort_by_rep.dta')
s <- read_dta('output/SCENARIO/ELSA_core_remove_smoken/ELSA_core_remove_smoken_by_rep.dta')

compareSurvivalCurve(c, s, 'No Smoking', save=FALSE)
```

@@

  # Had a small problem when trying to rename using the variable name given as function argument
  # Found solution here: https://stackoverflow.com/questions/49650394/how-to-rename-a-variable-using-a-dynamic-name-and-dplyr
  survivals <- survivals %>%
                 dplyr::rename('Age' = cohort.Age, 'Rep' = cohort.rep, 'Baseline' = cohort.Survival, !!quo_name(int_name) := intervention.Survival) %>%
                 melt(id.var = 'Age', value.name = 'Survival')

  p <-ggplot(data = survivals, aes(x=Age, y=Survival, color = variable)) +
        geom_line() +
        labs(x = 'Age', y = 'Survival')

@@

compareSurvivalCurveConfints(c_rep, s_rep)
```

### Lung Disease Prevalence All
```{r}
c <- c
s <- s

@@

>>>>

## Libraries
```{r "setup", include=FALSE}
require(tidyverse)
require(haven)
require(ggplot2)
require(Hmisc)
require(reshape2)

@@

## Heart Disease Intervention
```{r}
# compareDeathAge <- function(base, int, int_name, save=FALSE, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {
#   
#   aDeath <- data.frame(base$year, base$d_age_all, int$d_age_all)
#   
#   aDeath <- aDeath %>%
#                 dplyr::rename('Year' = base.year, 'Baseline' = base.d_age_all, !!quo_name(int_name) := int.d_age_all) %>%
#                 reshape2::melt(id.var = 'Year', value.name = 'Age')
#   
#   p1 <- ggplot(data = aDeath, aes(x = Year, y = Age, color = variable)) +
#         geom_smooth(lwd = 0.5, se=FALSE) +
#         labs(x = 'Year', y = 'Age at Death') +
#   
#   if(save) {
#     ggsave(filename = 'hearte_dAge_all.png',
#          plot = p1,
#          path = path)
#   }
#   
#   return(p1)
# }
```

### Life-Expectancy
```{r}
# b <- read_dta('output/SCENARIO/ELSA_core_base/ELSA_core_base_summary.dta')
# h_p <- read_dta('output/SCENARIO/ELSA_core_remove_hearte_p/ELSA_core_remove_hearte_p_summary.dta')
# 
# compareDeathAge(b, h_p, 'No Heart Disease', save=FALSE)
```

@@

### SplitbyEduc
```{r}
b <- b_rep
h <- h_rep

d.educ1 <- data.frame(b$year, b$rep, b$d_age_educ1, h$d_age_educ1)
d.educ1 <- d.educ1 %>%
                dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_educ1, 'Intervention' = h.d_age_educ1)
d.educ1.pivot <- pivot_longer(d.educ1,
                              cols = Baseline:Intervention,
                              names_to = 'Source',
                              values_to = 'Life_Expectancy')
p1 <- ggplot(data = d.educ1.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
      geom_smooth(lwd = 0.5) +
      labs(title = 'Low', x = 'Year', y = 'Life Expectancy')
p1

d.educ2 <- data.frame(b$year, b$rep, b$d_age_educ2, h$d_age_educ2)
d.educ2 <- d.educ2 %>%
                dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_educ2, 'Intervention' = h.d_age_educ2)
d.educ2.pivot <- pivot_longer(d.educ2,
                              cols = Baseline:Intervention,
                              names_to = 'Source',
                              values_to = 'Life_Expectancy')
p2 <- ggplot(data = d.educ2.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
      geom_smooth(lwd = 0.5) +
      labs(title = 'Moderate', x = 'Year', y = 'Life Expectancy') +
      scale_fill_grey()
p2

d.educ3 <- data.frame(b$year, b$rep, b$d_age_educ3, h$d_age_educ3)
d.educ3 <- d.educ3 %>%
                dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_educ3, 'Intervention' = h.d_age_educ3)
d.educ3.pivot <- pivot_longer(d.educ3,
                              cols = Baseline:Intervention,
                              names_to = 'Source',
                              values_to = 'Life_Expectancy')
p3 <- ggplot(data = d.educ3.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
      geom_smooth(lwd = 0.5) +
      labs(title = 'High', x = 'Year', y = 'Life Expectancy')
p3

path <- '/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/test/'

ggsave(filename = 'hearte_dAge_educ1.png',
         plot = p1,
         path = path)

ggsave(filename = 'hearte_dAge_educ2.png',
         plot = p2,
         path = path)

ggsave(filename = 'hearte_dAge_educ3.png',
         plot = p3,
         path = path)

## Smoking Intervention
```{r}
# compareSurvivalCurve <- function(cohort, intervention, int_name, save=FALSE,
#                                  path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {
#   
#   # Calculate age and survival curves
#   cohort$Age <- (cohort$year - 2012) + 50
#   intervention$Age <- (intervention$year - 2012) + 50
#   cohort$Survival <- cohort$m_endpop_all / cohort$m_endpop_all[1]
#   intervention$Survival <- intervention$m_endpop_all / intervention$m_endpop_all[1]
#   
#   survivals <- data.frame(cohort$Age, cohort$Survival, intervention$Survival)
#   
#   # Had a small problem when trying to rename using the variable name given as function argument
#   # Found solution here: https://stackoverflow.com/questions/49650394/how-to-rename-a-variable-using-a-dynamic-name-and-dplyr
#   survivals <- survivals %>%
#                  dplyr::rename('Age' = cohort.Age, 'Baseline' = cohort.Survival, !!quo_name(int_name) := intervention.Survival) %>%
#                  melt(id.var = 'Age', value.name = 'Survival')
#   
#   p1 <-ggplot(data = survivals, aes(x=Age, y=Survival, color = variable)) +
#         geom_line() +
#         labs(x = 'Age', y = 'Survival')
#   
#   if(save) {
#     ggsave(filename = paste0(int_name, '_survival_curve.png'),
#          plot = p1,
#          path = path)
#   }
#   
#   return(p1)
# }
```

### Survival Curve
```{r}
# c <- read_dta('output/SCENARIO/ELSA_core_cohort/ELSA_core_cohort_summary.dta')
# s <- read_dta('output/SCENARIO/ELSA_core_remove_smoken/ELSA_core_remove_smoken_summary.dta')
# 
# compareSurvivalCurve(c, s, 'No Smoking', save=FALSE)
```

@@

  # Had a small problem when trying to rename using the variable name given as function argument
  # Found solution here: https://stackoverflow.com/questions/49650394/how-to-rename-a-variable-using-a-dynamic-name-and-dplyr
  survivals <- survivals %>%
                 dplyr::rename('Age' = cohort.Age, 'Rep' = cohort.rep, 'Baseline' = cohort.Survival, !!quo_name(int_name) := intervention.Survival) %>%
                 pivot_longer(
                   cols = Baseline:'No Smoking',
                   names_to = 'Source',
                   values_to = 'Life_Exp'
                 )

  p <-ggplot(data = survivals, aes(x=Age, y=Life_Exp, color = Source)) +
        geom_smooth(lwd = 0.5) +
        labs(x = 'Age', y = 'Survival')

@@

compareSurvivalCurveConfints(c_rep, s_rep, 'No Smoking', save=TRUE)
```

### Lung Disease Prevalence All
```{r}
c <- read_dta('output/SCENARIO/ELSA_core_cohort/ELSA_core_cohort_summary.dta')
s <- read_dta('output/SCENARIO/ELSA_core_remove_smoken/ELSA_core_remove_smoken_summary.dta')

@@

#ggsave(filename = 'smok_lunge_all.png',
#         plot = p1,
#         path = path)
```

```{r}
c <- c_rep
s <- s_rep

d.all <- data.frame(c$Age, c$rep, c$p_lunge_all, s$p_lunge_all)
d.all <- d.all %>%
                dplyr::rename('Age' = c.Age, 'Rep' = c.rep, 'Baseline' = c.p_lunge_all, 'Intervention' = s.p_lunge_all)
d.all.pivot <- pivot_longer(d.all,
                              cols = Baseline:Intervention,
                              names_to = 'Source',
                              values_to = 'Prevalence')
p1 <- ggplot(data = d.all.pivot, aes(x = Age, y = Prevalence, color = Source)) +
      geom_smooth(lwd = 0.5) +
      labs(x = 'Age', y = 'Prevalence')
p1
